Fast, Scalable Phrase-Based SMT Decoding

### 2016-01-29 acl.2016/acl2016.tex
acl paper

The most popular stack configuration for phrase-based model, as implemented in Pharaoh, Moses and Joshua, has been by coverage cardinality, ie. hypotheses that have translated the same number of source words are stored in the same stack. There have been research into other stack layouts \citep{ortizmartinez-garciavarea-casacuberta:2006:WMT}, and it has been noted that the decoder described in (???IBM) uses coverage stacks, as opposed to coverage cardinality. We re-visit this issue by testing the advantages of stack coverage and cardinality layout.

@@

\bibliography{acl2016}
\bibliographystyle{acl2016}

>>>>

The most popular stack configuration for phrase-based model, as implemented in Pharaoh, Moses and Joshua, has been by coverage cardinality, ie. hypotheses that have translated the same number of source words are stored in the same stack. There have been research into other stack layouts ~\cite{ortizmartinez-garciavarea-casacuberta:2006:WMT}, and it has been noted that the decoder described in (???IBM) uses coverage stacks, as opposed to coverage cardinality. We re-visit this issue by testing the advantages of stack coverage and cardinality layout.

@@

\bibliography{acl2016,mt,more}
\bibliographystyle{acl2016}
